A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-20 writeup/paper.tex
Cropped completion time figure
Anonymized for submission

@@

%%%%%%%%%%%%%%% NAT LANG PIE TABLE %%%%%%%%%%%
\begin{figure}[h]
\footnotesize
\begin{tabular}{lrlrlr}\hline\hline
%Language&\# Turkers\\
\hline
English&591&	French&63&	Vietnamese&34\\
Tamil&253&	Polish&61&	Macedonian&31\\
Malayalam&219&	Urdu&56&	Cebuano&29\\
Hindi&149&	Tagalog&54&	Swedish&26\\
Spanish&131&	Marathi&48&	Bulgarian&25\\
Telugu&87&	Russian&44&	Hungarian&23\\
Chinese&86&	Italian&43&	Swahili&23\\
Romanian&85&	Bengali&41&	Thai&22\\
Portuguese&82&	Gujarati&39&	Catalan&22\\
Arabic&74&	Hebrew&38&	Lithuanian&21\\
Kannada&72&	Dutch&37&	Punjabi&21\\
German&66&	Turkish&35&	Others &$\leq$20\\
\hline\hline
\end{tabular}
\normalsize
\caption{Self-reported native language of 3,154 bilingual Turkers. Not shown are 54 langs with $\leq$20 speakers  each for a total of 423 remaining speakers.  We omit Turkers did not self-report their native languages (1,801), 243 who reported two native languages, 83 who reported $\geq$3 native languages.}\label{lang-pie}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We chose the languages which were highly used on Wikipedia, in terms of the number of available articles. We compiled a list of all languages for which there existed at least 10,000 Wikipedia articles; we also included a small number of low resource languages for which there were approximately 1,000 available articles, giving a total of 119 languages to use in our task. For each of the languages, we chose the 1,000 most popular articles, and from these selected the 10,000 most frequent words. The resulting vocabularies served as the source side of our dictionaries.

@@

%%%%%%%%%%%%%%% COMPLETION TIME CHART %%%%%%%%%%%
\begin{figure}[h]
\centering
\includegraphics[height=\linewidth,angle=270]{figures/completiontime}
\caption{Time (in days) to complete all HITs in each language. Red bar shows time until first HIT was started,
% relative to the time the first HIT in each language was started, relative to the time the first HIT in any language was started (first HIT started across all languages was Urdu). 
 blue bar shows time until all HITs in each language were completed.}
\label{completion-time}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

% Anonymized for submission
\author{}

@@

%%%%%%%%%%%%%%% NAT LANG PIE TABLE %%%%%%%%%%%
\begin{figure}[h]
\footnotesize
\begin{tabular}{lrlrlr}\hline\hline
%Language&\# Turkers\\
\hline
English&591&	French&63&	Vietnamese&34\\
Tamil&253&	Polish&61&	Macedonian&31\\
Malayalam&219&	Urdu&56&	Cebuano&29\\
Hindi&149&	Tagalog&54&	Swedish&26\\
Spanish&131&	Marathi&48&	Bulgarian&25\\
Telugu&87&	Russian&44&	Hungarian&23\\
Chinese&86&	Italian&43&	Swahili&23\\
Romanian&85&	Bengali&41&	Thai&22\\
Portuguese&82&	Gujarati&39&	Catalan&22\\
Arabic&74&	Hebrew&38&	Lithuanian&21\\
Kannada&72&	Dutch&37&	Punjabi&21\\
German&66&	Turkish&35&	Others &$\leq$20\\
\hline\hline
\end{tabular}
\normalsize
\caption{Self-reported native language of 3,154 bilingual Turkers. Not shown are 54 langs with $\leq$20 speakers  each. 
%(for a total of 423 remaining speakers).  
We omit 1,801 Turkers did not report their native language, 243 who reported 2 native languages, and 83 who reported $\geq$3 native languages.}\label{lang-pie}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We chose the languages which were highly used on Wikipedia, in terms of the number of available articles.\footnote{\url{http://meta.wikimedia.org/wiki/List_of_Wikipedias}} We compiled a list of all languages for which there existed at least 10,000 Wikipedia articles; we also included a small number of low resource languages for which there were approximately 1,000 available articles, giving a total of 119 languages to use in our task. For each of the languages, we chose the 1,000 most popular articles, and from these selected the 10,000 most frequent words. The resulting vocabulariesserved as the source side of our dictionaries.

@@

%%%%%%%%%%%%%%% COMPLETION TIME CHART %%%%%%%%%%%
\begin{figure}[h]
\centering
\includegraphics[height=\linewidth,angle=270]{figures/completiontime}
\caption{Time (in days) to complete all HITs in each language. Red bars show time until first HIT was started,
% relative to the time the first HIT in each language was started, relative to the time the first HIT in any language was started (first HIT started across all languages was Urdu). 
 blue bars show time until all HITs in each language were completed.}
\label{completion-time}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
